### 2017-11-14 framework/heuristic.tex
all-in-one
work

This heuristic states that the search should only
backtrack at most $k$ steps when the search gets stuck using only $E$.
The motivation is that many protocols operate as a sequence of independent
transactions, and the uncertainty of previous transactions often do not affect
the next transaction.
For instance, in 802.11 packet transmission protocol, each packet exchange,
include the original, retransmission and acknowledgment packets, constitute a
transaction.
And the retransmission status of previous packets has no effect on the packets
with subsequent sequence numbers, hence need not be explored when resolving the
uncertainty of the packets with new sequence numbers.  Note that we do not
require the protocol to specify an exact transaction boundary, but only need $k$
to be sufficiently large to cover a transaction.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.4\textwidth]{./figures/loss.pdf}
  \caption{\textbf{Example Sniffer Trace and Its Mutation Trace.}}
  \label{fig:loss}
\end{figure}

>>>>

This heuristic states that the search should only
backtrack at most $k$ steps when the search gets stuck using only $E$.
The motivation is that many protocols operate as a sequence of independent
transactions, and the uncertainty of previous transactions often does not affect
the next transaction.
For instance, in 802.11 packet transmission protocol, each packet exchange,
include the original, retransmission and acknowledgment packets, constitutes a
transaction.
And the retransmission status of previous packets has no effect on the packets
with subsequent sequence numbers, hence need not be explored when resolving the
uncertainty of the packets with new sequence numbers.  Note that we do not
require the protocol to specify an exact transaction boundary, but only need $k$
to be sufficiently large to cover a transaction.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.4\textwidth]{loss.pdf}
  \caption{\textbf{Example Sniffer Trace and Its Mutation Trace.}}
  \label{fig:loss}
\end{figure}

### 2017-11-14 introduction.tex
comments
work

We present a new technique than enables validation of protocol implementations using
wireless sniffers. Given a monitor state machine representing the protocol being
validated, we describe a systematic transformation that adds non-deterministic
transitions to incorporate uncertainty introduced by the sniffer. This
augmented validation state machine implicitly defines a set of
mutated traces, each satisfying the original state machine with a specific
likelihood. If the set is empty, the implementation definitely violates the
protocol. Searching over all the mutated traces is NP-complete, but the approach
can be made practical by applying protocol-oblivious heuristics that limit the
search to likely mutated traces.

>>>>

We present a new technique that enables validation of protocol implementations using
wireless sniffers. Given a monitor state machine representing the protocol being
validated, we describe a systematic transformation that adds non-deterministic
transitions to incorporate uncertainty introduced by the sniffer. This
augmented validation state machine implicitly defines a set of
mutated traces, each satisfying the original state machine with a specific
likelihood. If the set of mutated traces is empty, the implementation definitely violates the
protocol. Searching over all the mutated traces is NP-complete, but the approach
can be made practical by applying protocol-oblivious heuristics that limit the
search to likely mutated traces.
